Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-03-17 paper.qmd
Added function plot MSE

@@

error_plot_two_non_linear_diff_shaped_close_clusters <- ggplot(error_two_non_linear_diff_shaped_close_clusters, 
                           aes(x = a1, 
                               y = MSE, 
                               colour = method)) + 
  geom_point(size = 0.8) +
  geom_line(linewidth = 0.3) + 
  # geom_vline(xintercept = 15, linetype="solid", 
  #            color = "black", linewidth=0.8, alpha = 0.5) +
  scale_x_continuous(breaks = sort(unique(error_two_non_linear_diff_shaped_close_clusters$a1))[seq(1, length(unique(error_two_non_linear_diff_shaped_close_clusters$a1)), by = 5)]) +
  scale_color_manual(values=c('#e41a1c','#ff7f00','#4daf4a', "#a65628",'#636363', '#984ea3')) +
  scale_y_log10() +
  ylab("log(MSE)") +
  xlab(expression(paste("binwidth (", a[1], ")"))) +
  theme_minimal() +
  theme(panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 15, hjust = 0.5, vjust = -0.5),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line(),
        legend.position = "none",
        axis.text = element_text(size = 7),
        axis.title = element_text(size = 12))

@@

error_plot_pbmc <- ggplot(error_pbmc, 
                          aes(x = a1, 
                              y = MSE, 
                              colour = method)) + 
  geom_point(size = 0.8) +
  geom_line(linewidth = 0.3) + 
  scale_x_continuous(breaks = sort(unique(error_pbmc$a1))[c(1, 5, 9, 13, 17, 21, 26)]) +
  scale_color_manual(values=c('#e41a1c','#377eb8','#4daf4a','#ff7f00',
                              '#984ea3','#999999','#a65628','#f781bf')) +
  scale_y_log10() +
  ylab("log(MSE)") +
  xlab(expression(paste("binwidth (", a[1], ")"))) +
  theme_minimal() +
  theme(panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 12, hjust = 0.5, vjust = -0.5),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line(),
        legend.position = "none",
        axis.text.x = element_text(size = 7),
        axis.text.y = element_text(size = 7),
        axis.title.x = element_text(size = 7),
        axis.title.y = element_text(size = 7))

@@

error_plot_mnist <- ggplot(error_mnist, 
                          aes(x = a1, 
                              y = MSE, 
                              colour = method)) + 
  geom_point(size = 0.8) +
  geom_line(linewidth = 0.3) + 
  scale_x_continuous(breaks = sort(unique(error_mnist$a1))[append(seq(1, length(unique(error_mnist$a1)), by = 5), 24)]) +
  scale_color_manual(values=c('#e41a1c','#377eb8',"#ff7f00", '#984ea3', '#999999', '#a65628')) +
  scale_y_log10() +
  ylab("log(MSE)") +
  xlab(expression(paste("binwidth (", a[1], ")"))) +
  theme_minimal() +
  theme(panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 12, hjust = 0.5, vjust = -0.5),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line(),
        legend.position = "none",
        axis.text.x = element_text(size = 7),
        axis.text.y = element_text(size = 7),
        axis.title.x = element_text(size = 7),
        axis.title.y = element_text(size = 7))

>>>>

```{r}
#| label: plot-mse

plot_mse <- function(error_df) {

  ggplot(error_df, 
       aes(x = a1, 
           y = MSE, 
           colour = method)) + 
  geom_point(size = 0.8) +
  geom_line(linewidth = 0.3) + 
  scale_y_log10() +
  ylab("log(MSE)") +
  xlab(expression(paste("binwidth (", a[1], ")"))) +
  theme_minimal() +
  theme(panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 12, hjust = 0.5, vjust = -0.5),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line(),
        legend.position = "none",
        axis.text.x = element_text(size = 7),
        axis.text.y = element_text(size = 7),
        axis.title.x = element_text(size = 7),
        axis.title.y = element_text(size = 7))

@@

error_plot_two_non_linear_diff_shaped_close_clusters <-
  plot_mse(error_two_non_linear_diff_shaped_close_clusters) +
  scale_x_continuous(breaks = sort(unique(error_two_non_linear_diff_shaped_close_clusters$a1))[seq(1, length(unique(error_two_non_linear_diff_shaped_close_clusters$a1)), by = 5)]) +
  scale_color_manual(values=c('#e41a1c','#ff7f00','#4daf4a', "#a65628",'#636363', '#984ea3')) +
  scale_y_log10()

@@

error_plot_pbmc <- plot_mse(error_pbmc) +
  scale_x_continuous(breaks = sort(unique(error_pbmc$a1))[c(1, 5, 9, 13, 17, 21, 26)]) +
  scale_color_manual(values=c('#e41a1c','#377eb8','#4daf4a','#ff7f00',
                              '#984ea3','#999999','#a65628','#f781bf'))

@@

error_plot_mnist <- plot_mse(error_mnist) +
  scale_x_continuous(breaks = sort(unique(error_mnist$a1))[append(seq(1, length(unique(error_mnist$a1)), by = 5), 24)]) +
  scale_color_manual(values=c('#e41a1c','#377eb8',"#ff7f00", '#984ea3', '#999999', '#a65628'))
